Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-10-04 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/c37aaa8}{c37aaa8} on 2024-10-01 at 13:08:31 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/de1c340}{de1c340} on 2024-10-04 at 10:35:14 UTC.
